---
title: "dashboard-zero"
author: "gsilvapt"
date: "December 2015"
output: 
  html_document: 
    keep_md: yes
runtime: shiny
---

This page will provide all related information with MoFo metrics.
In this particular page, you will find all information related to [dashboard-zero project](https://github.com/adamlofting/dashboard-zero).

# Inputs

All data has been being retrieved running a few scripts, with the help of @drazisil.

<font color = "red">
Last update: --<br>
Next update: --</font>

```{r, echo=FALSE}
setwd("C:\\Users\\gusta_000\\Documents\\GitHub\\dashboard-zero\\data")
repos_data <- read.csv("repos.csv", header = T, sep ="," )
issues_data <- read.csv("issues.csv", header = T, sep = ",", stringsAsFactors = FALSE)
```

## Requests

The following list came from the developers team feedback.

1. Number of unanswered volunteer input in Github issues
2. Number of Pull Requests that have had no response at all
3. Number of Pull Requests that have had no activity for more than X days
4. Number of open bugs (total)
5. Number of bugs by triage status
6. Number of bugs assigned to expired Milestones

### 1 - Unanswered volunteer inputs

```{r, echo = FALSE}
sum(issues_data$comments_count == "0")
``` 

### 2 - Number of pull requests without response

Ordered by priority

```{r, echo=FALSE}
library(knitr)
showURL <- subset(issues_data, issues_data$comments_count > 0, select = c(title, comments_count, html_url))
kable(head(order_showURL <- showURL[, 2:3][order(showURL$comments_count, decreasing = FALSE), ], n = 151), format ="markdown")

#head(order_showURL, n = 151)
``` 

### 3 - Number of pull requests that have had no activity for more than X days 

*To be updated*

### 4 - Total number of open bugs

```{r, echo=FALSE}
sum(repos_data$open_issues)
```

### 5 - Triage status - top 20 projects with less updates
This bit of code consideres that is_pullRequest = TRUE

```{r, echo=FALSE}
library(knitr)
issues_data_isPull <- subset(issues_data, is_pullrequest == "true")
kable(head(ordered_by_lastUpdate <- issues_data_isPull[, 2:5 & 7][order(issues_data_isPull$updated_date, decreasing = FALSE), ], n=50), format = "markdown")

#head(ordered_by_lastUpdate, n = 20)
```

## Extra

A bit more information about all datasets we have including:
1. Top 10 projects with most bugs
2. Most used programming language

### 1 - Top 10 projects with most bugs
```{r, echo=FALSE}
repos_data_clean <- subset(repos_data, open_issues != "0")

head(ordered_by_issues <- repos_data_clean[order(repos_data_clean$open_issues, decreasing = TRUE), ], n=10)
#head(ordered_by_issues, n = 10)
```

### 2 - Most used programming language
```{r, echo=FALSE}
print("JavaScript")
sum(repos_data$language == "JavaScript")
print("Java")
sum(repos_data$language == "Java")
print("TypeScript")
sum(repos_data$language == "TypeScript")
print("Python")
sum(repos_data$language == "Python")
print("C")
sum(repos_data$language == "C")
print("C++")
sum(repos_data$language == "C++")
print("CSS")
sum(repos_data$language == "CSS")
print("HTML")
sum(repos_data$language == "HTML")
```


```{r, echo=FALSE}
#(Page layout and design)
```

rmarkdown::render("page.rmd")